---
title: "case_study"
author: "Sarah Haberlack"
date: "2023-10-10"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(ggridges)
library(leaflet)

data(nyc_airbnb)
nyc_airbnb =
  nyc_airbnb |> 
  rename(borough = neighbourhood_group) |> 
  mutate(stars = review_scores_location / 2)
```

```{r}
str(nyc_airbnb)
```

# Brainstorm questions
- Where are AirBNBs expensive?
  Borough? neighborhood?
  Do other factors (room type) affect price? What about rating?
- How long are AirBNBs active?
  Are AirBNBs illegal and do they get shut down?
- Which units have the most availability?
- How is review score impacted by location?
- How many apts are run by one host?

Look at it
```{r}
view(nyc_airbnb)

bronx = nyc_airbnb |> filter(borough == "Bronx")

fivestars = filter(nyc_airbnb)

```
 
## Do some EDA
```{r}
nyc_airbnb |> 
  count(borough)

nyc_airbnb |> 
  group_by(borough, room_type) |> 
  summarize(mean_price = mean(price)) |> 
  pivot_wider(
    names_from = room_type,
    values_from = mean_price
  )
```

```{r}
nyc_airbnb |> 
  group_by(borough, room_type) |> 
  summarize(median_price = median(price)) |> 
  pivot_wider(
    names_from = room_type,
    values_from = median_price
  )
```

```{r}
nyc_airbnb |> 
  ggplot(aes(x = price)) +
  geom_histogram() +
  facet_grid(borough ~ room_type)
```

```{r}
nyc_airbnb |> 
  filter(price >=9500)
```

```{r}
nyc_airbnb |> 
  filter(price < 1000, room_type == "Entire home/apt") |> 
  ggplot(aes(x = price)) +
  geom_histogram() +
  facet_grid(. ~ borough)
```

Take averages of lowest priced neighborhoods in manhattan.
```{r}
nyc_airbnb |> 
  filter(
    price < 1000,
    room_type == "Entire home/apt",
    borough == "Manhattan") |> 
  group_by(neighborhood) |> 
  summarize(
    n_apt = n(),
    mean_price = mean(price)) |> 
  arrange(desc(mean_price))
```


```{r}
nyc_airbnb |> 
  filter(
    price < 1000,
    room_type == "Entire home/apt",
    borough == "Manhattan") |>
  ggplot(aes(x = neighborhood, y = price)) +
  geom_boxplot()
```

That boxplot was alphabetically ordered. Unhelpful. Let's group neighborhoods by price, and figure out how to rearrange the graphs so that we can read the neighborhood names.
```{r}
nyc_airbnb |> 
  filter(
    price < 1000,
    room_type == "Entire home/apt",
    borough == "Manhattan") |>
  mutate(neighbourhood = fct_reorder(neighborhood, price)) |> 
  ggplot(aes(x = price, y = neighborhood)) +
  geom_density_ridges()
```

## Try to make a map
Because we have latitude and longitude, we can make maps!

```{r}
nyc_airbnb |> 
  filter(
    price < 1000,
    room_type == "Entire home/apt",
    borough == "Manhattan") |>
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point()
```

Try something else entirely.
Leaflet for mapping. teachdatascience.com
start with the df,
do leaflet or GGplot,
them you add geometry on top of that.
markers is likely adding the locations of the marks on the map. 
then add a location to long and lat.

```{r}
nyc_airbnb |> 
  filter(
    price < 1000,
    room_type == "Entire home/apt",
    borough == "Manhattan") |>
  sample_n(500) |> 
  leaflet() |> 
addProviderTiles(providers$CartoDB.Positron) |> 
  addCircleMarkers(~long, ~lat, radius = .5)
  
```

